Dark matter halo concentrations with a bayesian approach

### 2014-09-08 paper/article.tex
corrected mistake in mock haloes
added correction

We generate $100$ mock halos with concentration values randomly
placed in the range $1<c<10$. Each one of the halos is generated with
four different total particle numbers: $20$, $200$, $2000$ and $20000$.

@@

In Figure \ref{fig:error} we plotted $\xi$ for the three methods. We consider that $\xi$ is a good estimate because it is standardized, giving equal weight to all errors regardless of the magnitude of the concentrations or the number of halos. On the other hand we have that $\xi$ decreases quite fast with the number of particles and is more precise in any case that the other methods.

>>>>

We generate $100$ mock halos with concentration values randomly
placed in the range $1<c<20$. Each one of the halos is generated with
four different total particle numbers: $20$, $200$, $2000$ and $20000$.

@@

In Figure \ref{fig:error} we plotted $\xi$ for the three methods. We consider that $\xi$ is a good estimate because it is standardized, giving equal weight to all errors regardless of the magnitude of the concentrations or the number of halos. On the other hand we have that $\xi$ decreases quite fast with the number of particles for our method and is more precise in any case that the other methods.
